Effectiveness of community-based TURF-reserves in Mexican small-scale fisheries

### 2019-01-27 docs/manuscript.tex
Uncorporated changes from Stuart and Rev2 and re-submitted

Marine ecosystems around the world sustain significant impacts due to
overfishing and unsustainable fishing practices
\citep{pauly_2005-qV,worm_2006-IB,halpern_2008-dK}. In particular,
small-scale fisheries face great challenges since they tend to be hard
to monitor and enforce \citep{costello_2012}. One of the many approaches
taken to improve the performance of coastal fisheries and health of the
local resources is through the implementation of Territorial Use Rights
for Fisheries (TURFs) that contain no-take marine reserves within them,
thus creating TURF-reserve systems
\citep{afflerbach_2014,gelcich_2015,lester_2017}.

TURFs are a fisheries management tool in which a well defined group of
fishers (\emph{e.g.} fishing cooperatives) have exclusive access to an
explicitly delimited portion of the ocean. They promote a sense of
stewardship and incentivise resource users to sustainably manage their
resources \citep{gelcich_2008,costello_2010,mccay_2014}. On the other
hand, no-take marine reserves (marine reserves from hereinafter) are
areas where all extractive activities are off-limits. These can be
implemented to protect biodiversity but also as fishery management tools
to aid in the recovery of marine stocks. These instruments can be
combined by establishing a marine reserve within a TURF, thus making
them TURF-reserves \citep{afflerbach_2014,gelcich_2015,lester_2017}.

Conservation science has shown how marine reserves lead to increased
biomass, species richness, and abundance within the protected regions
\citep{lester_2009}, and that these may have a series of additional
benefits like climate change mitigation, protection from environmental
variability, and fisheries benefits
\citep{roberts_2017-J9,micheli_2012-EU,krueck_2017-J1}. Likewise,
research on TURFs has shown that these areas have higher abundance of
targeted species than sites operating under open access and even similar
to that of marine reserves \citep{gelcich_2008,gelcich_2012}. The
benefits resulting from reserves established within TURFs (\emph{i.e.}
TURF-reserves) should be captured exclusively by the group of fishers
with exclusive access \citep{gelcich_2015}. Although in theory these
systems are successful \citep{smallhornwest_2018}, there is little
empirical evidence of their effectiveness and the drivers of their
success. Moreover, TURF-reserve systems are inherently intricate
social-ecological systems, and their effectiveness must depend on how
environmental and social factors combine and interact
\citep{ostrom_2009,gelcich_2015}. It is therefore important to consider
not only the indicators of interest, bu also the governance settings
under which the reserves occur.

@@

Before discussing our data collection methods and describing our
analyses, our case studies warrant some more background. Community-based
marine reserves that are implemented within TURFs are a form of
TURF-reserves, voluntarily established and enforced by local
communities. This bottom-up approach increases compliance and
self-enforcement, and reserves can yield benefits similar to
systematically-designed reserves \citep{beger_2004,smallhornwest_2018}.
Community-based spatial closures occur in different contexts, like the
\emph{kapu} or \emph{ra'ui} areas in the Pacific Islands
\citep{bohnsack_2004,johannes_2002}. However, community-based reserves
can be hard to enforce if they are not legally recognized. In such
conditions, TURF fishers must rely on the exclusive access of the TURF
to maintain high levels of compliance.

In an effort to bridge this normative gap, Mexican Civil Society
Organizations (CSOs) served as a link between fishers and government,
and created a legal framework that solves this governance issue: Fish
Refuges \citep{nom}. Fish Refuges can be implemented as temporal or
partial reserves, which can protect one, some, or all resources within
their boundaries. One of the ways in which fishing communities have
taken advantage of this new tool is by implementing temporal marine
reserves within their TURFs with a defined expiration date (often 5
years). When the expiration date is reached, fishers can chose to open
the reserves to fishing or re-establish them. Our work focuses on Fish
Refuges implemented as community-based TURF-reserves that occur in
small-scale fisheries.

The common setup of community-based TURF-reserves in Mexico is the
following. Fishers from a given community are assembled in fishing
cooperatives which have exclusive fishing rights over a spatially
delimited area (\emph{i.e.} TURFs shown as blue polygons in Fig
\ref{fig:map}A). Each TURF is exclusively fished by one cooperative, and
each community usually hosts no more than one cooperative. The profits
from each TURF are shared amongst all fishers from the cooperative.
Fishing cooperatives interested in implementing marine reserves work
with CSOs to implement marine reserves within their TURFs (\emph{i.e.}
TURF-reserves). Fishers then ask the government to grant legal
recognition to their TURF-reserves as Fish Refuges following a series of
studies outlined in the regulation \citep{nom}.

@@

We evaluate three community-based no-take TURF-reserves implemented in
Mexican TURF-managed fisheries, therefore making them TURF-reserves (Fig
\ref{fig:map}A). The first one was created by the \emph{Buzos y
Pescadores de la Baja California} fishing cooperative, located in Isla
Natividad in the Baja California Peninsula (Fig \ref{fig:map}B). The
main fishery in the island is the spiny lobster (\emph{Panulirus
interruptus}), but other resources like finfish, sea cucumber, read sea
urchin, snail, and abalone are also an important source of income. In
2006, the community decided to implement two marine reserves within
their fishing grounds. The objective of these reserves was ``to protect
commercially important invertebrate species''; mainly lobster and
abalone. These reserves obtained legal recognition in 2018
\citep{dof_website_2018}.

The other two TURF-reserves are located in Maria Elena and Punta
Herrero, in the Yucatan Peninsula (Fig \ref{fig:map}C). In contrast with
Isla Nativdad, which hosts a well established fishing community, Maria
Elena is a fishing camp --visited intermittently during the fishing
season-- belonging to the \emph{Cozumel} fishing cooperative; Punta
Herrero is home to the \emph{José María Azcorra} fishing cooperative,
and similar to Isla Natividad hosts a local community. Their main
fishery is the Caribbean spiny lobster (\emph{Panulirus argus}), but
they also target finfish in the off-season. Maria Elena and Punta
Herrero established eight and four marine reserves in 2012 and 2013,
respectively. These reserves have been legally recognized as Fishing
Refuges since their original implementation
\citep{dof_website_2012,dof_website_2013} and subsequent
re-establishments \citep{dof_website_2017b}.

@@

We use three main sources of information to evaluate these reserves
across the ecological, socioeconomic, and governance dimensions.
Ecological data come from the annual ecological monitoring of reserve
and control sites. Reserve sites are areas where no fishing occurs.
Control sites are areas that meet the following criteria: i) habitat
characteristics are similar to the corresponding reserves, ii)
presumably had a similar probability of being selected as reserves
during the design phase, iii) are located within the TURF, where fishing
occurs, and iv) Are not directly adjacent to the reserves. We focus our
evaluation on sites where data are available for reserve and control
sites, before and after the implementation of the reserve. This provides
us with a Before-After-Control-Impact (\emph{i.e.} BACI) sampling design
that allows us to capture and control for temporal and spatial dynamics
\citep{stewartoaten_1986,depalma_2018} and causally attribute the
changes to the reserve
\citep{francinifilho_2008,Villasenor-Derbez_2018}.

@@

The coefficient interpretations remains as for Eq. \ref{eqn:reg_bio},
but in this case the \(Treated\) dummy variable indicates if the
community has a reserve (\(Treated = 1\)) or not (\(Treated = 0\)).
These regression models allow us to establish a causal link between the
implementation of marine reserves and the observed trends by accounting
for temporal and site-specific dynamics \citep{depalma_2018}. We fit one
model per community and indicators (\emph{e.g.} there are three models
for lobster density, one for each community) for a total of 12
biological model fits and four socioeconomic model fits. Model
coefficients were estimated via ordinary least-squares and used
heteroskedastic-robust standard errors \citep{zeileis_2004-7n}. All
analyses were performed in R version 3.5.1 and R Studio version 1.1.456
\citep{R_2018}. All data and code needed to reproduce our analyses are
available in a GitHub repository at:
\url{https://github.com/jcvdav/ReserveEffect}.

@@

The following sections present the effect that marine reserves had on
each of the biological and socioeconomic indicators for each coastal
community. Results are presented in terms of the difference through time
and across sites, relative to the control site on the year of
implementation (\emph{i.e.} the difference-in-differences estimate or
effect size \(\lambda_t\) from Eqs. \ref{eqn:reg_bio} and
\ref{eqn:soc_reg}). We also provide an overview of the governance
settings of each community, and discuss how these might be related to
the effectiveness and performance of the reserves.

@@

Lobster landings and revenue were only available for Isla Natividad and
Maria Elena (Fig \ref{fig:lobsters}). For all years before
implementation, the effect sizes are close to zero, indicating that the
control and treatment sites have similar pre-treatment trends,
suggesting that these are plausible controls. However, effect sizes do
not change after the implementation of the reserve. Interestingly, the
negative effect observed for Isla Natividad on year 5 correspond to the
2011 hypoxia events. The only positive change observed in lobster
landings is for Isla Natividad in 2014 (\(p < 0.1\)). The three years of
post-implementation data for Maria Elena do not show a significant
effect of the reserve. Isla Natividad shows higher revenues after the
implementation of the reserve, as compared to the control communities.
However, these changes are only significant for the third year
(\(p < 0.05\)). Full tables with model coefficients are presented in the
supplementary materials (Tables S4-S5).

@@

Our analysis of the SES (Table \ref{table:ses}) shows that all analyzed
communities share similarities known to foster sustainable resource
management and increase reserve effectiveness. For example, fishers
operate within clearly outlined TURFs (RS2, GS6.1.4.3) that provide
exclusive access to resources and reserves. Along with their relatively
small groups (A1 - Number of relevant actors), Isolation (A3),
Operational rules (GS6.2), Social monitoring (GS9.1), and Graduated
sanctions (GS10.1), these fisheries have solid governance structures
that enable them to monitor their resources and enforce rules to ensure
sustainable management. In general, success of conservation initiatives
depends on the incentives of local communities to maintain a healthy
status of the resources upon which they depend \citep{jupiter_2017}. Due
to the clarity of access rights and isolation, the benefits of
conservation directly benefit the members of the fishing cooperatives,
which have favored the development of efficient community-based
enforcement systems. However, our SES analysis also highlights factors
that might hinder reserve performance or mask outcomes. While total
reserve size ranges from 0.2\% to 3.7\% of the TURF area, individual
reserves are often small (RS3); the largest reserve is only 4.37 km
\textsuperscript{2}, and the smallest one is 0.09 km
\textsuperscript{2}. Reserves are also relatively young (RS5).
Additionally, fishers harvest healthy stocks (RS4.1), and it's unlikely
that marine reserves will result in increased catches.

@@

Another key condition for effectiveness is reserve size
\citep{edgar_2014-UO}, and the lack of effectiveness can perhaps be
attributed to poor ecological coherence in reserve design (\emph{sensu}
\citet{rees_2018}). Previous research has shown that reserves in Isla
Natividad yield fishery benefits for the abalone fishery
\citep{rossetto_2015-V0}. Abalone are less mobile than lobsters, and
perhaps the reserves provide enough protection to these sedentary
invertebrates, but not lobsters. Design principles developed by
\citet{green_2017} for marine reserves in the Caribbean state that
reserves ``should be more than twice the size of the home range of
adults and juveniles'', and suggest that reserves seeking to protect
spiny lobsters should have at least 14 km across. Furthermore, fishers
may favor implementation of reserves that pose low fishing costs due to
their small size or location. Our analysis of economic data supports
this hypothesis, as neither landings nor revenues showed the expected
short-term reductions associated to the first years of reserve
implementation \citep{ovando_2016-Wg}.

@@

Finally, extreme conditions, including prolonged hypoxia, heat waves,
and storms have affected both the Pacific and Caribbean regions, with
large negative impacts of coastal marine species and ecosystems
\citep{cavole_2016,hughes_2018,breitburg_2018}. The coastal ecosystems
where these reserves are located have been profoundly affected by these
events \citep{micheli_2012-EU,woodson_2018}. Effects of protection might
be eliminated by the mortalities associated with these extreme
conditions.

While the evaluated reserves have failed to provide fishery benefits up
to now, there are a number of additional ecological, fisheries, and
social benefits. Marine reserves provide protection to a wider range of
species and vulnerable habitat. Previous research focusing on these
specific sites has shown that they serve as an insurance mechanism
against uncertainty and errors in fisheries management, as well as mild
environmental shocks
\citep{micheli_2012-EU,deleo_2015,roberts_2017-J9,aalto}.
Self-regulation of fishing effort can serve as a way to compensate for
future declines associated to environmental variation
\citep{finkbeiner_2018}. Furthermore, embarking in a marine conservation
project can bring the community together, which promotes social cohesion
and builds social capital \citep{fulton_2019}. Showing commitment to
marine conservation and sustainable fishing practices has allowed
fishers to have greater bargaining power and leverage over fisheries
management \citep{prezramrez_2012}. These additional benefits might
explain why communities show a positive perception about their
performance and continue to support their presence by re-implementing
the reserves \citep{ayer_2018}.

Community-based TURF-reserves in small-scale fisheries may be helpful
conservation and fishery management tools when appropriately implemented
\citep{gelcich_2015}. We must promote bottom-up design and
implementation processes like the ones in the evaluated reserves, but
without setting design principles aside. Having full community support
surely represents an advantage, but it is important that community-based
TURF-reserves meet essential design principles such as size and
placement so as to maximize their effectiveness. Furthermore, consvation
and advocacy groups should consider the opportunity costs of such
interventions (\emph{sensu} \citet{smith_2010}) and evaluate the
potential of other approaches that may yield similar benefits.

In terms of the fisheries regulation in Mexico, our work only evaluates
Fish Refuges established within TURFs. Future research should aim at
evaluating other Fish Refuges established as bottom-up processes but
without the presence of TURFs (\emph{e.g.} \citet{dof_websiteC_2012}),
others established through top-down processes (\emph{i.e.}
\citet{dof_websiteU_2018}), as well as the relationship between
governance and effectiveness across this gradient of approaches. For the
particular case of the reserves that we evaluate, the possibility of
expanding reserves or merging existing polygons into larger areas should
be evaluated and proposed to the communities.

@@

The authors wish to acknowledge Imelda Amador for contributions on the
governance data, as well as pre-processing biological data. This study
would have not been possible without the effort by members of the
fishing communities here mentioned, who participated in the
data-collection process. The authors wish to acknowledge comments by the
reviewrs and editor, which significantly improved the quality of this
work.

>>>>

Marine ecosystems around the world sustain significant impacts due to
overfishing and unsustainable fishing practices
\citep{pauly_2005-qV,worm_2006-IB,halpern_2008-dK}. In particular,
small-scale fisheries face great challenges since they tend to be hard
to monitor and enforce \citep{costello_2012}. One of the many approaches
taken to improve the performance of coastal fisheries and health of the
local resources is through the implementation of Territorial Use Rights
for Fisheries (TURFs) that contain no-take marine reserves, thus
creating TURF-reserve systems
\citep{afflerbach_2014,gelcich_2015,lester_2017}.

TURFs are a fisheries management tool in which a well-defined group of
fishers (\emph{e.g.} fishing cooperatives) have exclusive access to an
explicitly delimited portion of the ocean. They promote a sense of
stewardship and incentivise resource users to sustainably manage their
resources \citep{gelcich_2008,costello_2010,mccay_2014}. On the other
hand, no-take marine reserves (marine reserves from hereinafter) are
areas where all extractive activities are off-limits. These can be
implemented to protect biodiversity but also as fishery management tools
to aid in the recovery of marine stocks. These instruments can be
combined by establishing a marine reserve within a TURF, thus making
them TURF-reserves \citep{afflerbach_2014,gelcich_2015,lester_2017}.

Conservation science has shown how marine reserves lead to increased
biomass, species richness, and abundance within the protected regions
\citep{lester_2009}, and that these may have a series of additional
benefits such as climate change mitigation, protection from
environmental variability, and fisheries benefits
\citep{roberts_2017-J9,micheli_2012-EU,krueck_2017-J1}. Likewise,
research on TURFs has shown that these areas have higher abundance of
targeted species than sites operating under open access and even similar
to that of marine reserves \citep{gelcich_2008,gelcich_2012}. The
benefits resulting from reserves established within TURFs (\emph{i.e.}
TURF-reserves) should be captured exclusively by the group of fishers
with exclusive access \citep{gelcich_2015}. Although in theory these
systems are successful \citep{smallhornwest_2018}, there is little
empirical evidence of their effectiveness and the drivers of their
success. Moreover, TURF-reserve systems are inherently intricate
social-ecological systems, and their effectiveness must depend on how
environmental and social factors combine and interact
\citep{ostrom_2009,gelcich_2015}. It is therefore important to consider
not only the indicators of interest, but also the governance settings
under which the reserves operate.

@@

Before discussing our data collection methods and describing our
analyses, our case studies warrant some background. Community-based
marine reserves that are implemented within TURFs are a form of
TURF-reserve, voluntarily established and enforced by local communities.
This bottom-up approach increases compliance and self-enforcement, and
reserves can yield benefits similar to systematically-designed reserves
\citep{beger_2004,smallhornwest_2018}. Community-based spatial closures
occur in different contexts, like the \emph{kapu} or \emph{ra'ui} areas
in the Pacific Islands \citep{johannes_2002,bohnsack_2004}. However,
community-based reserves can be hard to enforce if they are not legally
recognized. In such conditions, TURF fishers must rely on the exclusive
access of the TURF to maintain high levels of compliance.

In an effort to bridge this normative gap, Mexican Civil Society
Organizations (CSOs) served as a link between fishers and government,
and helped create a legal framework that solves this governance issue:
Fish Refuges \citep{nom}. Fish Refuges can be implemented as permanent,
temporary or partial reserves, which can protect one, some, or all
resources within their boundaries. One of the ways in which fishing
communities have taken advantage of this new tool is by implementing
temporary marine reserves within their TURFs with a defined expiration
date (often five years). When the expiration date is reached, fishers
can chose to open the reserves to fishing or re-establish them. Our work
focuses on Fish Refuges implemented as community-based TURF-reserves in
small-scale fisheries.

The most common setup of community-based TURF-reserves in Mexico is the
following. Fishers from a given community are assembled in fishing
cooperatives which have exclusive fishing rights over a spatially
delimited area (\emph{i.e.} TURFs shown as blue polygons in Fig
\ref{fig:map}A). Each TURF is exclusively fished by one cooperative, and
each community usually hosts no more than one cooperative. The profits
from each TURF are shared amongst all fishers from the cooperative.
Fishing cooperatives interested in implementing marine reserves work
with CSOs to implement marine reserves within their TURFs (\emph{i.e.}
TURF-reserves). Fishers then ask the government to grant legal
recognition to their TURF-reserves as Fish Refuges following a series of
studies outlined in the regulation \citep{nom}.

@@

We evaluate three community-based no-take TURF-reserve systems
implemented in Mexican TURF-managed fisheries, therefore making them
TURF-reserves (Fig \ref{fig:map}A). The first one was created by the
\emph{Buzos y Pescadores de la Baja California} fishing cooperative,
located in Isla Natividad in the Baja California Peninsula (Fig
\ref{fig:map}B). The main fishery in the island is the spiny lobster
(\emph{Panulirus interruptus}), but other resources like finfish, sea
cucumber, sea urchin, snail, and abalone are also an important source of
income. In 2006, the community decided to implement two marine reserves
within their fishing grounds. The objective of these reserves was ``to
protect commercially important invertebrate species''; mainly lobster
and abalone. The reserves obtained legal recognition in 2018
\citep{dof_website_2018}.

The other two TURF-reserve systems are located in Maria Elena and Punta
Herrero, in the Yucatan Peninsula (Fig \ref{fig:map}C). In contrast with
Isla Nativdad, which hosts a well-established fishing community, Maria
Elena is a fishing camp visited intermittently during the fishing season
that belongs to the \emph{Cozumel} fishing cooperative. Punta Herrero is
home to the \emph{José María Azcorra} fishing cooperative, and similar
to Isla Natividad hosts a small community. Their main fishery is the
Caribbean spiny lobster (\emph{Panulirus argus}), but they also target
finfish in the off-season. Maria Elena and Punta Herrero established
eight and four marine reserves in 2012 and 2013, respectively. These
reserves have been legally recognized as Fishing Refuges since their
original implementation \citep{dof_website_2012,dof_website_2013} and
subsequent re-establishments \citep{dof_website_2017b}.

@@

We use three main sources of information to evaluate these reserves
across ecological, socioeconomic, and governance dimensions. Ecological
data come from the annual ecological monitoring of reserve and control
sites. Reserve sites are areas where no fishing occurs. Control sites
are areas that meet the following criteria: i) habitat characteristics
are similar to the corresponding reserves, ii) presumably had a similar
probability of being selected as reserves during the design phase, iii)
are located within the TURF, where fishing occurs, and iv) are not
directly adjacent to the reserves. We focus our evaluation on sites
where data are available for reserve and control sites, before and after
the implementation of the reserve. This provides us with a
Before-After-Control-Impact (\emph{i.e.} BACI) sampling design that
allows us to capture and control for temporal and spatial dynamics
\citep{stewartoaten_1986,depalma_2018} and causally attribute the
changes to the reserve
\citep{francinifilho_2008,Villasenor-Derbez_2018}.

@@

The coefficient interpretations remains as for Eq. \ref{eqn:reg_bio},
but in this case the \(Treated\) dummy variable indicates if the
community has a reserve (\(Treated = 1\)) or not (\(Treated = 0\)).
These regression models allow us to establish a causal link between the
implementation of marine reserves and the observed trends by accounting
for temporal and site-specific dynamics \citep{depalma_2018}. We fit one
model per community and indicators (\emph{e.g.} there are three models
for lobster density, one for each community) for a total of 12
biological model fits and four socioeconomic model fits. Model
coefficients were estimated via ordinary least-squares and used
heteroskedastic-robust standard errors \citep{zeileis_2004-7n}. All
analyses were performed in R version 3.5.2 and R Studio version 1.1.456
\citep{R_2018}. All data and code needed to reproduce our analyses are
available in a GitHub repository at:
\url{https://github.com/jcvdav/ReserveEffect}.

@@

The following sections present the effect that marine reserves had on
the biological and socioeconomic indicators for each coastal community.
Results are presented in terms of difference through time and across
sites, relative to the control site on the year of implementation
(\emph{i.e.} the difference-in-differences estimate or effect size
\(\lambda_t\) from Eqs. \ref{eqn:reg_bio} and \ref{eqn:soc_reg}). We
also provide an overview of the governance settings of each community,
and discuss how these might be related to the effectiveness and
performance of the reserves.

@@

Lobster landings and revenue were only available for Isla Natividad and
Maria Elena (Fig \ref{fig:lobsters}). For all years before
implementation, the effect sizes are close to zero, indicating that the
control and treatment sites have similar pre-treatment trends,
suggesting that these are plausible controls. However, effect sizes do
not change after the implementation of the reserve. Interestingly, the
negative effect observed for Isla Natividad on year 5 corresponds to the
2011 hypoxia events \citep{micheli_2012-EU}. The only positive change
observed in lobster landings is for Isla Natividad in 2014
(\(p < 0.1\)). The three years of post-implementation data for Maria
Elena do not show a significant effect of the reserve. Isla Natividad
shows higher revenues after the implementation of the reserve, as
compared to the control communities. However, these changes are only
significant for the third year (\(p < 0.05\)). Full tables with model
coefficients are presented in the supplementary materials (Tables
S4-S5).

@@

Our analysis of the SES (Table \ref{table:ses}) shows that all analyzed
communities share similarities known to foster sustainable resource
management and increase reserve effectiveness. For example, fishers
operate within clearly outlined TURFs (RS2, GS6.1.4.3) that provide
exclusive access to resources and reserves. Along with their relatively
small groups (A1 - Number of relevant actors), Isolation (A3),
Operational rules (GS6.2), Social monitoring (GS9.1), and Graduated
sanctions (GS10.1), these fisheries have solid governance structures
that enable them to monitor their resources and enforce rules to ensure
sustainable management. In general, success of conservation initiatives
depends on the incentives of local communities to maintain a healthy
status of the resources upon which they depend \citep{jupiter_2017}. Due
to the clarity of access rights and isolation, the benefits of
conservation directly benefit the members of the fishing cooperatives,
which have favored the development of efficient community-based
enforcement systems. However, our SES analysis also highlights factors
that might hinder reserve performance or mask outcomes. While total
reserve size ranges from 0.2\% to 3.7\% of the TURF area, individual
reserves are often small (RS3); the largest reserve is only 4.37 km
\textsuperscript{2}, and the smallest one is 0.09 km
\textsuperscript{2}. Reserves are also relatively young (RS5).
Additionally, fishers harvest healthy stocks (RS4.1), and it is unlikely
that marine reserves will result in increased catches.

@@

Another key condition for effectiveness is reserve size
\citep{edgar_2014-UO}, and the lack of effectiveness can perhaps be
attributed to poor ecological coherence in reserve design (\emph{sensu}
\citet{rees_2018}). Previous research has shown that reserves in Isla
Natividad yield fishery benefits for the abalone fishery
\citep{rossetto_2015-V0}, however, abalone are less mobile than
lobsters, and perhaps the reserves provide enough protection to these
sedentary invertebrates, but not lobsters. Design principles developed
by \citet{green_2017} for marine reserves in the Caribbean state that
reserves ``should be more than twice the size of the home range of
adults and juveniles'', and suggest that reserves seeking to protect
spiny lobsters should have at least 14 km across. Furthermore, fishers
may favor implementation of reserves that pose low fishing costs due to
their small size or location. Our analysis of economic data supports
this hypothesis, as neither landings nor revenues showed the expected
short-term reductions associated to the first years of reserve
implementation \citep{ovando_2016-Wg}.

@@

Finally, extreme conditions, including prolonged hypoxia, heat waves,
and storms have affected both the Pacific and Caribbean regions, with
large negative impacts on coastal marine species and ecosystems
\citep{cavole_2016,hughes_2018,breitburg_2018}. The coastal ecosystems
where these reserves are located have been profoundly affected by these
events \citep{micheli_2012-EU,woodson_2018}. Effects of protection might
be eliminated by the mortalities associated with these extreme
conditions.

While the evaluated reserves have failed to provide fishery benefits to
date, there are a number of additional ecological, fisheries, and social
benefits. Marine reserves provide protection to a wider range of species
and vulnerable habitat. Previous research focusing on these specific
sites has shown that they serve as an insurance mechanism against
uncertainty and errors in fisheries management, as well as mild
environmental shocks
\citep{micheli_2012-EU,deleo_2015,roberts_2017-J9,aalto}.
Self-regulation of fishing effort can serve as a way to compensate for
future declines associated to environmental variation
\citep{finkbeiner_2018}. Furthermore, embarking on a marine conservation
project can bring the community together, which promotes social cohesion
and builds social capital \citep{fulton_2019}. Showing commitment to
marine conservation and sustainable fishing practices has allowed
fishers to have greater bargaining power and leverage over fisheries
management \citep{prezramrez_2012}. These additional benefits might
explain why communities show a positive perception about their
performance and continue to support their presence by re-implementing
the reserves \citep{ayer_2018}.

Community-based TURF-reserves in small-scale fisheries may be helpful
conservation and fishery management tools when appropriately implemented
\citep{gelcich_2015}. We must promote bottom-up design and
implementation processes like the ones in the evaluated reserves, but
without setting design principles aside. Having full community support
surely represents an advantage, but it is important that community-based
TURF-reserves meet essential design principles such as size and
placement so as to maximize their effectiveness. Furthermore,
conservation and advocacy groups should consider the opportunity costs
of such interventions (\emph{sensu} \citet{smith_2010}) and evaluate the
potential of other approaches that may yield similar benefits.

In terms of fisheries regulation in Mexico, our work only evaluates Fish
Refuges established within TURFs. Future research should aim at
evaluating other Fish Refuges established as bottom-up processes but
without the presence of TURFs (\emph{e.g.} \citet{dof_websiteC_2012}),
others established through top-down processes (\emph{i.e.}
\citet{dof_websiteU_2018}), as well as the relationship between
governance and effectiveness across this gradient of approaches. For the
particular case of the reserves that we evaluate, the possibility of
expanding reserves or merging existing polygons into larger areas should
be evaluated and proposed to the communities.

@@

The authors wish to acknowledge Imelda Amador for contributions on the
governance data, as well as pre-processing biological data. This study
would have not been possible without the effort by members of the
fishing communities here mentioned, who participated in the
data-collection process. The authors wish to acknowledge comments by the
reviewers and editor, which significantly improved the quality of this
work.
